The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
hab sel scale

@@

<!-- McGarigal 2016 organisms select habitat at multiple scales, temporal spatial 
should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics
MRSF Laforge paper 
van Beest et al. 2014 scale paper 
Habitat–performance relationships: finding the right metric at a given spatial scale
Multi-scale habitat selection modeling: a review and outlook
-->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales. Habitat selection is often
measured using resource selection functions (RSFs) and species distribution
models (SDMs). Both of these methods are based on the proportion of used
resources and available resources for an animal. Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, (3) the habitat patches within the home range and
(4) specific resources within a habitat patch. Extending beyond this
hierarchical perspective, Mayor (2009) reviewed scale in habitat selection and

@@

we could define layers of the multilayer network according to home range overlap 
instead of specific associations
looking at broader temporal scales and coarser spatial resolutions
-->
How to combine moving forward: habitat selection, space use, multiple scales, multilayer networks
Sociality across scales eg home range overlap and interactions
Layers defined by habitat/landcover

>>>>

The link between habitat and sociality has been

@@

<!-- McGarigal 2016 organisms select habitat at multiple scales, temporal spatial
should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics

Mayor 2007 - scale paper
MRSF Laforge paper 
van Beest et al. 2014 scale paper 
Habitat–performance relationships: finding the right metric at a given spatial scale
Multi-scale habitat selection modeling: a review and outlook
-->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, (3)
the habitat patches within the home range and (4) specific resources within a
habitat patch. Moving past this hierarchical perspective, Mayor (2009)
reviewed types of scale relevant in measurement of habitat selection and recommend using a continuum of scales for identifying characteristic scales of selection. For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviours.

@@

we could define layers of the multilayer network according to home range overlap 
instead of specific associations
looking at broader temporal scales and coarser spatial resolutions
-->

conversely, one might envision generating a multilayer network where
nodes are individual patches
selection,
similarity, 
connectivity

How to combine moving forward: habitat selection, space use, multiple scales, multilayer networks
Sociality across scales eg home range overlap and interactions
Layers defined by habitat/landcover
